A hierarchical model to evaluate pest treatments from prevalence and intensity data

### 2023-10-06 submitted-202310-favrot-pest.qmd
try to trigger the action

keywords: [bayesian model, epidemiology, hierarchical model, pest control, trial, survey]
doi: "to complete"
citation:
  type: article-journal
  container-title: "Computo"
  issued: "2023/01/25"
  url: https://computo.sfds.asso.fr/
  issn: "2824-7795"
google-scholar: true
bibliography: references.bib
github-user: computorg
repo: "To complete"
draft: true 
published: false
format:
  computo-html: default
  computo-pdf: default
header-includes:
  - \usepackage{lineno}
---

>>>>

keywords: [bayesian model, epidemiology, hierarchical model, pest control, trial, survey]
doi: "to complete"
citation:
  type: article-journal
  container-title: "Computo"
  issued: "2023/01/25"
  url: https://computo.sfds.asso.fr/
  issn: "2824-7795"
google-scholar: true
bibliography: references.bib
github-user: computorg
repo: "To complete"
draft: true 
published: false
format:
  computo-html: default
  computo-pdf: default
---
